---
title: "Super Bowl Ads"
author: "Mandy Norrbo"
output:
  html_document:
    theme: journal
    highlight: haddock
    toc: true
    toc_float: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# About the dataset

This dataset was sourced from [rfordatascience/tidytuesday](https://github.com/rfordatascience/tidytuesday) and contains information on Super Bowl commercials. 

<details>
<summary>**Data Dictionary**</summary>
|**variable**                  |**class**     |**description** |
|:-------------------------|:---------|:-----------|
|year                      |double    | Superbowl year |*
|brand                     |character | Brand for commercial |
|*superbowl_ads_dot_com_url* |character | Superbowl ad URL |
|*youtube_url*               |character | Youtube URL |
|*funny*                     |logical   | Contains humor |
|*show_product_quickly*      |logical   | Shows product quickly |
|*patriotic*                 |logical   | Patriotic |
|*celebrity*                 |logical   | Contains celebrity |
|*danger*                    |logical   | Contains danger |
|*animals*                   |logical   | Contains animals |
|*use_sex*                   |logical   | Uses sexuality |
|*id*                        |character | Youtube ID |
|*kind*                      |character | Youtube Kind |
|*etag*                      |character | Youtube etag |
|*view_count*                |integer   | Youtube view count |
|*like_count*                |integer   | Youtube like count |
|*dislike_count*             |integer   | Youtube dislike count |
|*favorite_count*            |integer   | Youtube favorite count |
|*comment_count*             |integer   | Youtube comment count |
|*published_at*              |character | Youtube when published |
|*title*                     |character | Youtube title |
|*description*               |character | Youtube description |
|*thumbnail*                 |character | Youtube thumbnail |
|*channel_title*             |character | Youtube channel name |
|*category_id*               |character | Youtube content category id |
</details>



# Dependencies and data

```{r}
library(tidyverse)
library(tidytext)
library(ggtext)
library(patchwork)
library(knitr)
library(kableExtra)

superbowl_ads <- read_csv("data/youtube.csv")
```

# Ad content visualisation

## Reshaping

```{r}
ads_long <- superbowl_ads %>% 
  select(-show_product_quickly) %>% 
  pivot_longer(
    cols = funny:use_sex,
    names_to = "contains_category",
    values_to = "contains_value"
  ) 

ad_content <- ads_long %>% 
  group_by(contains_category, contains_value) %>% 
  summarise(avg_likes = mean(like_count, na.rm = T)) %>% 
  group_by(contains_category) %>% 
  # create lgl col that is TRUE when contains TRUE avg_likes > contains FALSE avg_likes
  # i.e. whether the ad should contain the thing to get more likes
  mutate(should_contain = avg_likes - lag(avg_likes) > 0) %>%
  fill(should_contain, .direction = "up") %>% 
  mutate(
    contains_category = recode(
      contains_category,
      animals = "Ad contains animals",
      celebrity = "Ad contains celebrity",
      danger = "Ad contains danger",
      patriotic = "Ad is patriotic",
      use_sex = "Ad uses sexuality",
      funny = "Ad contains humour"
      ),
    contains_value = as.character(contains_value),
    contains_value = recode(
      contains_value,
      "TRUE" = "Yes",
      "FALSE" = "No"
      ),
    contains_value = factor(contains_value, levels = c("Yes", "No"))
    )

```

## Custom theme
```{r}
ad_content_theme <- function() {
  theme_minimal() %+replace% 
        theme(plot.title = element_text(size = 16),
              strip.background = element_rect(fill = "#B0B7BD", colour = "white"))
}
```

## Create visualisation

```{r}
g1 <- ad_content %>% 
  filter(should_contain == TRUE) %>% 
  ggplot() +
  aes(x = contains_value, y = avg_likes, fill = contains_value) +
  geom_col() +
  facet_wrap(~contains_category) +
  labs(x = element_blank(),
       title = "In ads, **celebrities**, **danger** and **patriotism** are liked<br>",
       y = "Number of likes") +
  scale_fill_manual(values = c("Yes" = "#0A2342", "No" = "#C81F32"),
                    guide = "none") +
  ad_content_theme() +
  ylim(0, 8000) +
  theme(
    plot.title = element_markdown()
  )
  

g2 <- ad_content %>% 
  filter(should_contain == FALSE) %>% 
  ggplot() +
  aes(x = contains_value, y = avg_likes, fill = contains_value) +
  geom_col() +
  facet_wrap(~contains_category) +
  labs(x = element_blank(),
       title = "Whereas, **animals**, **humour** and **sexuality** are not<br>",
       y = "Number of likes",
       caption = "**Source**: *Super Bowl ads on YouTube*") +
  scale_fill_manual(values = c("Yes" = "#0A2342", "No" = "#C81F32"),
                    guide = "none") +
  ad_content_theme() +
  ylim(0, 8000) +
  theme(
    plot.title = element_markdown(),
    plot.caption = element_markdown()
  )


g1 / g2
```


```{r}
ggsave(filename="plots/ad_content.png", 
       device="png", 
       height=5, 
       width=8, 
       units="in", 
       dpi=500)
```

# Engagement across brands

```{r}
superbowl_ads %>% 
  arrange(year) %>% 
  mutate(ad_id = row_number()) %>% 
  select(ad_id, year, brand, title, like_count, dislike_count, view_count, comment_count) %>% 
  drop_na() %>% 
  pivot_longer(
    cols = like_count:comment_count,
    names_to = "count_category",
    values_to = "count"
  ) %>% 
  group_by(year, brand, count_category) %>% 
  summarise(total_count = sum(count)) %>% 
  ggplot() +
  aes(x = year, y = total_count, group = brand, colour = brand) +
  geom_line() +
  facet_wrap(~count_category, scales = "free_y")
```

# Highest dislike to like ratio

```{r}
superbowl_ads %>% 
  arrange(year) %>% 
  mutate(ad_id = row_number()) %>% 
  select(ad_id, year, brand, title, like_count, dislike_count) %>% 
  drop_na() %>% 
  pivot_longer(
    cols = like_count:dislike_count,
    names_to = "count_category",
    values_to = "count",
    names_pattern = "(.*)_count" # get rid of suffix
  ) %>%
  group_by(ad_id) %>% 
  mutate(ratio = count/lag(count)) %>%
  drop_na() %>% 
  filter(is.finite(ratio)) %>% 
  select(-count) %>% 
  group_by(year) %>% 
  slice_max(ratio, n = 1) %>% 
  ggplot(aes(x = year, y = ratio, colour = brand)) +
  geom_jitter() +
  geom_label(aes(label = brand))
```



# Text mining

## Recoding video categories

```{r}
ad_text <- superbowl_ads %>% 
  mutate(ad_id = row_number()) %>% 
  select(ad_id, year, brand, title, description, category_id) %>% 
  mutate(
    category_id = as.character(category_id),
    # source: https://gist.github.com/dgp/1b24bf2961521bd75d6c#gistcomment-2714395
    video_category = case_when(
      category_id == "1" ~ "Film & Animation",
      category_id == "2" ~ "Autos & Vehicles",
      category_id == "10" ~ "Music",
      category_id == "15" ~ "Pets & Animals",
      category_id == "17" ~ "Sports",
      category_id == "18" ~ "Short Movies",
      category_id == "19" ~ "Travel & Events",
      category_id == "20" ~ "Gaming",
      category_id == "21" ~ "Videoblogging",
      category_id == "22" ~ "People & Blogs",
      category_id == "23" ~ "Comedy",
      category_id == "24" ~ "Entertainment",
      category_id == "25" ~ "News & Politics",
      category_id == "26" ~ "Howto & Style",
      category_id == "27" ~ "Education",
      category_id == "28" ~ "Science & Technology",
      category_id == "29" ~ "Nonprofits & Activism",
      category_id == "30" ~ "Movies",
      category_id == "31" ~ "Anime/Animation",
      category_id == "32" ~ "Action/Adventure",
      category_id == "33" ~ "Classics",
      category_id == "34" ~ "Comedy",
      category_id == "35" ~ "Documentary",
      category_id == "36" ~ "Drama",
      category_id == "37" ~ "Family",
      category_id == "38" ~ "Foreign",
      category_id == "39" ~ "Horror",
      category_id == "40" ~ "Sci-Fi/Fantasy",
      category_id == "41" ~ "Thriller",
      category_id == "42" ~ "Shorts",
      category_id == "43" ~ "Shows",
      category_id == "44" ~ "Trailers",
      TRUE ~ "Unknown"
  ))

```

## Top TF-IDF scores across video categories

```{r}
# nothing interesting from descriptions/titles with year, category, brand as document
ad_text %>% 
  unnest_tokens(
    word,
    description # or title
  ) %>% 
  count(
    video_category, # or year, brand
    word, 
    sort = T) %>% 
  bind_tf_idf(
    word,
    video_category,
    n
  ) %>% 
  group_by(video_category) %>% 
  slice_max(tf_idf, with_ties = F) %>% 
  arrange(desc(n)) %>% 
  select(video_category, word, n, tf_idf) %>% 
  filter(!is.na(word)) %>% 
  mutate(tf_idf = round(tf_idf, 3)) %>%
  kbl() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
  
```


