---
title: "Seattle Pets"
author: "Mandy"
date: "19/05/2020"
output: html_document
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
```


### Variables in this dataset

* `license_issue_date` contains the date the animal was registered with Seattle
* `license_number`	is a unique license number
* `animals_name`	is the pet's name
* `species`	is the species of the animal (dog, cat, goat, etc)
* `primary_breed`	is the primary breed of the animal
* `secondary_breed`	is the secondary breed if mixed
* `zip_code`	is the zip code the animal is registered under

### Dependencies
```{r}
library(tidyverse)
library(GGally)
library(janitor)
library(lubridate)
library(patchwork)
library(bbplot)
library(colorspace)
library(gghighlight)
```

### Loading in the data
```{r}
seattle_pets <- read_csv("data/seattle_pets.csv")

```

### Gender names
```{r}
baby_names <- read_csv("data/baby_names.csv")

baby_names <- baby_names %>% 
  select(sex, animals_name = FirstForename) %>% 
  group_by(sex, animals_name) %>% 
  count() %>% 
  pivot_wider(names_from = sex, values_from = n)

baby_names[is.na(baby_names)] <- 0

baby_names <- baby_names %>% 
  mutate(perc_boy = (B/(B+G))) %>% 
  mutate(gender = ifelse(perc_boy > 2/3, "Boy", ifelse(perc_boy < 2/3 & perc_boy > 1/3, "Unisex", "Girl")))

pet_babies <- left_join(seattle_pets, baby_names) %>% 
  mutate(gender = replace_na(gender, replace = "Other"))


```






### Pets per month
```{r}

seattle_pets_monthly <- seattle_pets %>% 
  #filter(species %in% c("Cat", "Dog")) %>% 
  mutate(date = mdy(seattle_pets$license_issue_date)) %>% 
  mutate(month = month(date, label = T, abbr =F)) %>% 
  mutate(year = year(date)) %>% 
  filter(species %in% c("Cat", "Dog")) %>% 
  filter(year > 2014) %>% 
 # unite(col = "month_year", c(month, year), sep = " ") %>% 
  group_by(year) %>% 
  count(species)


top_10_cat_names <- seattle_pets %>% 
  filter(species == "Cat") %>% 
  na.omit %>% 
  group_by(animals_name) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  ungroup() %>% 
  slice(1:10)

top_10_dog_names <- seattle_pets %>% 
  filter(species == "Dog") %>% 
  na.omit %>% 
  group_by(animals_name) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  ungroup() %>% 
  slice(1:10)

common_top_names <- intersect(top_10_cat_names$animals_name, top_10_dog_names$animals_name)

dog_plot <- top_10_dog_names %>% 
  ggplot(aes(x = reorder(animals_name, -n), y = n)) +
  geom_col(aes(fill = animals_name)) +
  bbc_style() +
  theme(legend.position = "none", axis.title.y = element_blank(), 
        axis.title.x = element_blank()) +
  gghighlight(animals_name %in% common_top_names) +
  scale_fill_discrete_diverging(palette = "Berlin") +
  labs(title = "Top 10 Dog Names")

cat_plot <- top_10_cat_names %>% 
  ggplot(aes(x = reorder(animals_name, -n), y = n)) +
  geom_col(aes(fill = animals_name)) +
  bbc_style() +
  theme(legend.position = "none", axis.title.y = element_blank(), 
        axis.title.x = element_blank()) +
  gghighlight(animals_name %in% common_top_names) +
  scale_fill_discrete_diverging(palette = "Berlin") +
  labs(title = "Top 10 Cat Names")

dog_plot/cat_plot

```

```{r, echo = F, include = F}
ggsave(filename="plots/seattle_pet_names.png", 
       device="png", 
       height=5, 
       width=10, 
       units="in", 
       dpi=500)

```
