---
title: "Art Collections"
author: "Mandy Norrbo"
output:
  html_document:
    theme: journal
    highlight: haddock
    toc: true
    toc_float: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


# About the dataset


This dataset was sourced from [rfordatascience/tidytuesday](https://github.com/rfordatascience/tidytuesday) and contains metadata for around 70,000 artworks that Tate Art Museum owns or jointly owns.


<details>
<summary>**Data Dictionary**</summary>

<br>

`artwork.csv`

|**variable**           |**class**     |**description** |
|:------------------|:---------|:-----------|
|*id*                 |double    | Unique ID |
|*accession_number*   |character | Accession number |
|*artist*             |character | Artist Name |
|*artistRole*         |character | Artist or other attribution |
|*artistId*           |double    | Artist ID |
|*title*              |character | Title of the piece of art |
|*dateText*           |character | Date as raw text (pretty messy) |
|*medium*             |character | Medium of art, quite a lot of overlap |
|*creditLine*         |character | How acquired |
|*year*               |double    | Year of creation |
|*acquisitionYear*    |double    | Year acquired |
|*dimensions*         |character | Dimensions as character |
|*width*              |double    | Width of art |
|*height*             |double    | Height of art |
|*depth*              |double    | Depth of art |
|*units*              |character | units of measure |
|*inscription*        |character | inscription if present |
|*thumbnailCopyright* |logical   | Thumbnail copyright|
|*thumbnailUrl*       |character | Thumbnail URL |
|*url*                |character | art URL |

`artists.csv`

|variable     |class     |description |
|:------------|:---------|:-----------|
|*id*           |double    | Artist ID |
|*name*         |character | Artist Name |
|*gender*       |character | Artist gender|
|*dates*        |character | Date as a character |
|*yearOfBirth*  |double    | Year of birth |
|*yearOfDeath*  |double    | Year of death |
|*placeOfBirth* |character | Place of birth (typically city, country) |
|*placeOfDeath* |character | Place of death (typically city, country) |
|*url*          |character | Artist URL |

</details>

# Dependencies & Data

```{r}
library(tidyverse)
library(tidytext)
library(janitor)
library(ggwordcloud)

artists <- read_csv("data/artist_data.csv") %>% clean_names()
artwork <- read_csv("data/artwork.csv") %>% clean_names()

# join by name
joined_name <- inner_join(artists, artwork, by = c("name" = "artist"))
```


```{r, eval = F, include = F}

# having fun with purrr to check missing values
list(artists, artwork, joined_name) %>% 
  map(~summarise(.x, across(.fns = ~sum(is.na(.)))))

```

# Plan

- Artists: Year of birth and death, place of birth and death
- Artwork title: text - gender of artist?
- Artwork medium - gender? artist with most different mediums?
- width & height - smallest and largest artwork?
- difference between year and acquisition year?

```{r}
subset_df <- joined_name %>% 
  select(-c(id.x, dates, url.x, id.y, accession_number, artist_id, date_text, dimensions, units, thumbnail_url, thumbnail_copyright, url.y))

subset_df %>% names()
```

# Artists that died where they were born
```{r}
staying_artists <- subset_df %>% 
  select(name, gender, place_of_birth, place_of_death) %>% 
  filter(place_of_birth == place_of_death) %>% 
  distinct(name, place_of_birth)

staying_artists
```

# Artists that died young
```{r}
died_young <- subset_df %>% 
  select(name, gender, year_of_birth, year_of_death) %>%
  distinct() %>% 
  mutate(age_at_death = year_of_death - year_of_birth) %>% 
  filter(age_at_death > 15 & age_at_death < 120) %>% 
  select(name, age_at_death) %>% 
  slice_min(age_at_death, n = 50) %>% 
  pull(name)

died_young
```

```{r}
subset_df %>% 
  select(name, gender, title, year) %>% 
  unnest_tokens(
    word,
    title
  ) %>% 
  count(year, word, sort = T) %>% 
  bind_tf_idf(
    word,
    year,
    n
  ) %>% 
  group_by(year) %>% 
  slice_max(tf_idf) %>% 
  select(year, word, n, tf_idf) %>% 
  filter(n > 10,
         !(word %in% c("blank", "untitled", "no"))) %>% 
  arrange(desc(tf_idf))
```

```{r}
subset_df %>% 
  select(name, gender, title, year) %>% 
  unnest_tokens(
    bigram,
    title,
    token = "ngrams",
    n = 2
  ) %>% 
  count(year, bigram, sort = T) %>% 
  bind_tf_idf(
    bigram,
    year,
    n
  ) %>% 
  group_by(year) %>% 
  slice_max(tf_idf) %>% 
  select(year, bigram, n, tf_idf) %>% 
  arrange(desc(n)) 
```

```{r}
subset_df %>% 
  select(name, gender, title, year) %>% 
  unnest_tokens(
    word,
    title
  ) %>% 
  count(name, word, sort = T) %>% 
  bind_tf_idf(
    word,
    name,
    n
  ) %>% 
  group_by(name) %>% 
  slice_max(tf_idf, n = 1, with_ties = F) %>% 
  select(name, word, n, tf_idf) %>% 
  anti_join(stop_words) %>% 
  filter(!(word %in% c("title", "untitled", "blank")),
         n > 1) %>% 
  arrange(desc(n), desc(tf_idf))
```

```{r}

art_subjects <- subset_df %>% 
  select(name, gender, title, year) %>% 
  unnest_tokens(
    bigram,
    title,
    token = "ngrams",
    n = 2
  ) %>% 
  separate(bigram, c("word_1", "word_2"), sep = " ") %>% 
  filter(word_1 == "of") %>%
  count(word_1, word_2, sort = TRUE) %>% 
  anti_join(stop_words, by = c("word_2" = "word")) %>% 
  slice(-1) %>% 
  slice_max(n, n = 50) %>% 
  select(-word_1)

```


```{r}
gender_words <- subset_df %>% 
  select(gender, title) %>% 
  filter(gender %in% c("Male", "Female")) %>% 
  unnest_tokens(
    word,
    title
  ) %>% 
  count(gender, word, sort = T) %>% 
  bind_tf_idf(
    word,
    gender,
    n
  ) %>% 
  inner_join(get_sentiments("bing")) %>% 
  group_by(gender) %>% 
  slice_max(n, n = 50, with_ties = F) %>% 
  select(gender, word, sentiment, n)%>% 
  group_by(gender) %>% 
  mutate(n_perc = n/sum(n)) %>% 
  ungroup()
```

```{r}
gender_words %>% 
  unite(
    col = gender_sentiment,
    c(gender, sentiment),
    sep = "_",
    remove = F
  ) %>% 
ggplot(
  aes(label = word, size = n_perc, color = gender_sentiment)) +
  geom_text_wordcloud() +
  scale_size_area(max_size = 10) +
  theme_minimal() +
  theme(strip.text = element_text(size = 20, face = "bold")) +
  facet_wrap(~gender) +
  scale_color_manual(values = c(
    "#6b2a59",
    "#ed47be",
    "#22375c",
    "#4783ed"
  ))

```

